\documentclass[12pt]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{csquotes}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}

\title{
    \hfill \normalsize\today \\
    \textbf{\Large Articles to be Reviewed}\\[0.5em]
    \large IE-517 -- Closed-Loop Supply Chain Management}
    \author{\normalsize\fbox{
        \begin{tabular}{c@{\hspace{1cm}}c}
            Emek Irmak & Furkan Ertürk \\
            2444693 & 2740215 \\
        \end{tabular}
    }
        \date{}
}

\begin{document}

\maketitle
\onehalfspacing

\paragraph{} The following journal articles have been selected for the literature review on \enquote{Design of Logistics Networks in Closed-Loop Supply Chains}.

\begin{enumerate}
    \item \textbf{Fleischmann, M., Bloemhof-Ruwaard, J. M., Dekker, R., Van der Laan, E., Van Nunen, J. A., \& Van Wassenhove, L. N. (1997). Quantitative models for reverse logistics: A review. European journal of operational research, 103(1), 1-17.} \\[0.5em]
    {\small Reviews quantitative models for planning and improving reverse logistics, offering useful approaches for designing networks that handle returns and recovery activities.}

    \item \textbf{Srivastava, S. K. (2008). Network design for reverse logistics. Omega, 36(4), 535-548.} \\[0.5em]
    {\small Discusses models and strategies for designing reverse logistics networks, helping to structure systems that efficiently manage the flow of returned products.}

    \item \textbf{Lieckens, K., \& Vandaele, N. (2007). Reverse logistics network design with stochastic lead times. Computers \& Operations Research, 34(2), 395-416.} \\[0.5em]
    {\small Models a reverse logistics network under uncertainty, particularly focusing on stochastic lead times for returned products.}

    \item \textbf{Melo, M. T., Nickel, S., \& Saldanha-Da-Gama, F. (2009). Facility location and supply chain management–A review. European journal of operational research, 196(2), 401-412.} \\[0.5em]
    {\small Surveys facility location models in supply chain management, highlighting how network design must evolve when incorporating reverse logistics.}

    \item \textbf{Salema, M. I. G., Barbosa-Povoa, A. P., \& Novais, A. Q. (2007). An optimization model for the design of a capacitated multi-product reverse logistics network with uncertainty. European journal of operational research, 179(3), 1063-1077.} \\[0.5em]
    {\small The authors propose a mixed-integer linear programming model to design a reverse logistics network with multiple products and uncertain parameters.}

    \item \textbf{Jayaraman, V., Patterson, R. A., \& Rolland, E. (2003). The design of reverse distribution networks: models and solution procedures. European journal of operational research, 150(1), 128-149.} \\[0.5em]
    {\small This paper develops models and heuristic algorithms for designing efficient reverse logistics networks, focusing on remanufacturing and disposal.}

    \item \textbf{Ferri, G. L., Chaves, G. D. L. D., \& Ribeiro, G. M. (2015). Reverse logistics network for municipal solid waste management: The inclusion of waste pickers as a Brazilian legal requirement. Waste Management, 40, 173-191.} \\[0.5em]
    {\small A practical case study illustrating how reverse logistics networks are implemented for municipal waste collection and recycling in Brazil.}

    \item \textbf{Govindan, K., Soleimani, H., \& Kannan, D. (2015). Reverse logistics and closed-loop supply chain: A comprehensive review to explore the future. European journal of operational research, 240(3), 603-626.} \\[0.5em]
    {\small This recent and influential paper provides a detailed review of CLSC research trends, gaps, and future research directions, especially in network design and sustainability.}

    \item TODO
    
    \item TODO
\end{enumerate}

\section*{Classification}

The selected papers can be classified broadly into the following categories:

\begin{itemize}
    \item \textbf{Review Papers:} TODO
    \item \textbf{Model Development Papers:} TODO
    \item \textbf{Case Study Applications:} TODO
    \item \textbf{Focused Topic Studies (Reverse Logistics Network Design):} TODO
\end{itemize}


\end{document}
